Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-26 docs/paper.tex
Updated future work to reflect new ideas

	\subsubsection{MDD generation for matching}
	To generate MDDs for MAPFM, each agent also has to consider not one goal but all matching goals. To do this, the MDD construction following the breadth-first search has to be changed: each goal becomes an endpoint from which paths to the start node are traced, resulting in an MDD with one start node and one or more terminal nodes.
	\begin{wrapfigure}{R}{.35\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/path}
		\caption{Pathological case for ICTS-m}
		\label{fig:path}
	\end{wrapfigure}
	\subsubsection{Pathological case}
	\label{pathology}
	As a consequence of the $\min$ operation in the root definition, a pathological case can be derived. Consider a team of 4 agents $a_1^1$ through $a_4^1$. Let them be arranged in a configuration as depicted in Figure \ref{fig:path}. All four agents match the colour of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$. The optimal solution however is $(1,3,3,3)$ with SIC $10$ numbering the agents clockwise, meaning that $\Delta = 6$. It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed. As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
	%\subsubsection{Inverted MDD search}
	%The uniqueness of goals guarantees the existence of a goal node without vertex conflicts in searching MDDs in MAPF. In MAPFM, this is not the case and causes joint MDDs to be searched fully without finding a result. In addition, even if there exists a goal node, many of the paths represented by the joint MDD lead to conflicting maximal-depth nodes.

@@

	%\section{Future work}
	A key idea for future research to look into is how to exploit the lower-bound on solution SIC that can be found using the Hungarian Algorithm \cite{kuhn55}. This lower-bound could be used in a branch-and-bound \cite{land1960} search of matchings. The most straightforward way would be to use an algorithm for MAPF at leaf nodes but algorithms for MAPFM could be used to solve (small) branches. Another possibility would be to use this bound to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound. Lower-bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using a similar approach as \cite{baauw2021}. As long as there is a team that does not meet its bound, branching only on agents within this team is possible without losing optimality.

@@

	Lastly, more experimentation is needed to reach definite conclusions about how simple child pruning compares to existing pruning techniques for ICTS, which could be done by reproducing the ICTS pruning technique experiments reported in \cite{sharon2011} extended with simple child pruning variants. %Given that simple pruning is somewhat cheap computationally, it might also be possible to prune the child generation using simple child pruning but still use enhanced pruning to decide whether to execute $k$-agent low-level search, combining the benefits of searching a smaller ICT and performing fewer $k$-agent searches.

>>>>

	\subsubsection{MDD generation for matching}
	To generate MDDs for MAPFM, each agent also has to consider not one goal but all matching goals. To do this, the MDD construction following the breadth-first search has to be changed: each goal becomes an endpoint from which paths to the start node are traced, resulting in an MDD with one start node and one or more terminal nodes.
	\begin{wrapfigure}{R}{.35\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/path}
		\caption{Pathological case for ICTS-m}
		\label{fig:path}
	\end{wrapfigure}
	\subsubsection{Pathological case}
	\label{pathology}
	As a consequence of the $\min$ operation in the root definition, a pathological case can be derived. Consider a team of 4 agents $a_1^1$ through $a_4^1$. Let them be arranged in a configuration as depicted in Figure \ref{fig:path}. All four agents match the color of the centre goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$. The optimal solution however is $(1,3,3,3)$ with SIC $10$ numbering the agents clockwise, meaning that $\Delta = 6$. It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed. As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the 'limbs' of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
	%\subsubsection{Inverted MDD search}
	%The uniqueness of goals guarantees the existence of a goal node without vertex conflicts in searching MDDs in MAPF. In MAPFM, this is not the case and causes joint MDDs to be searched fully without finding a result. In addition, even if there exists a goal node, many of the paths represented by the joint MDD lead to conflicting maximal-depth nodes.

@@

	%\section{Future work}
	A key idea for future research to look into is how to exploit the (inclusive) lower-bound on solution SIC that can be found using the Hungarian Algorithm \cite{kuhn55} or similar methods like the JVC algorithm \cite{jonker1987}. This lower-bound could be used in a branch-and-bound \cite{land1960} search of matchings. An algorithm for MAPF could be used at leaf nodes as in exhaustive ICTS; however, solving (small) branches as MAPFM instances using approaches other than branch-and-bound is also a direction to explore. To retain the benefits of ordered enumeration and to potentially allow for a higher degree of bounding, an optimized version \cite{miller1997} of Murty's algorithm \cite{murty1968} for ranking all matchings in increasing order of cost could be taken as a starting point for such a branch-and-bound approach.

	%in which matchings are enumerated in increasing order of SIC

	%for MAPFM could be used to solve (small) branches.

	%The most straightforward way would be to use an algorithm for MAPF at leaf nodes but algorithms for MAPFM could be used to solve (small) branches.

	%Specifically,

	%By using the Hungarian Algorithm to determine

	%The most straightforward way would be to use an algorithm for MAPF at leaf nodes but algorithms for MAPFM could be used to solve (small) branches.

	Another possibility would be to use the lower-bound on solution SIC to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound. Lower-bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using an approach similar to those described in \cite{baauw2021}. As long as there is a team that does not meet its bound, branching only on agents within this team is possible without losing optimality.

@@

	Lastly, more experimentation is needed to reach definite conclusions about how simple child pruning compares to existing pruning techniques for ICTS, which could be done by reproducing the ICTS pruning experiments reported in \cite{sharon2011} extended with simple child pruning variants.

	%Given that simple pruning is somewhat cheap computationally, it might also be possible to prune the child generation using simple child pruning but still use enhanced pruning to decide whether to execute $k$-agent low-level search, combining the benefits of searching a smaller ICT and performing fewer $k$-agent searches.
